Emulsions Stabilized by Magnetic Ellipsoidal Particles: A Lattice Boltzmann Study

### 2025-04-11 chapters/lit_review_new.tex
adjusted footnote

@@

Additionally, the bijel itself was first realized computationally using LB simulations. \cite{stratford_colloidal_2005} A multicomponent LB model with neutrally wetting colloids based on the 
implementationby Ladd showed that coarsening interfaces could catch particles irreversibly adsorbing them and arresting coarsening once the interfacial area matched the cross sectional area of 
particles adsorbed \cite{stratford_colloidal_2005,ladd_numerical_1994}. The simulations also showed that these structures were stable over long periods of time, motivating and guiding the 
experimental realization of bijels in 2007 \cite{herzig_bicontinuous_2007}. These simulations provided an explanation of the dynamics and mechanistic reasoning behind the formation of bijels, 
allowing for the prediction of the microstructure. More recent LB studies have extended these findings by identifying the volume fraction and wetting angle needed to form bijels as opposed to 
Pickering emulsions \cite{jansen_bijels_2011}. The effect of the surface tension, fluid density and volume fraction of particles were also studied, showing that surface tension and fluid density 
had little effect on the microstructure of bijels and that the length scale of the bijel was inversely proportional to the volume fraction of particles \cite{jansen_bijels_2011}.

>>>>

\textcolor{blue}{add surface tension calculation}

\textcolor{blue}{add interface width calculation}

@@

Additionally, the bijel itself was first realized computationally using LB simulations. \cite{stratford_colloidal_2005} A multicomponent LB model with neutrally wetting colloids based on the 
implementation by Ladd showed that coarsening interfaces could catch particles irreversibly adsorbing them and arresting coarsening once the interfacial area matched the cross sectional area of 
particles adsorbed \cite{stratford_colloidal_2005,ladd_numerical_1994}. The simulations also showed that these structures were stable over long periods of time, motivating and guiding the 
experimental realization of bijels in 2007 \cite{herzig_bicontinuous_2007}. These simulations provided an explanation of the dynamics and mechanistic reasoning behind the formation of bijels, 
allowing for the prediction of the microstructure. More recent LB studies have extended these findings by identifying the volume fraction and wetting angle needed to form bijels as opposed to 
Pickering emulsions \cite{jansen_bijels_2011}. The effect of the surface tension, fluid density and volume fraction of particles were also studied, showing that surface tension and fluid density 
had little effect on the microstructure of bijels and that the length scale of the bijel was inversely proportional to the volume fraction of particles \cite{jansen_bijels_2011}.
